\documentclass[a4paper,10pt]{article}

\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{multicol}

% Page layout
\geometry{
    left=1.2cm,
    right=1.2cm,
    top=1.5cm,
    bottom=1.7cm
}
\setlength{\parskip}{0.4em}
\setlength{\parindent}{0pt}

% Colors and section formatting
\definecolor{darkblue}{RGB}{0, 51, 102}
\titleformat{\section}
  {\large\bfseries\color{darkblue}}
  {}
  {0em}
  {}
  [\titlerule]

\titlespacing*{\section}{0pt}{8pt}{4pt}

% Global bullet formatting
\setlist[itemize]{noitemsep, topsep=0pt, left=0pt}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\Huge \textbf{Shubham Jangra}} \\
    \vspace{1mm}
    \small{
        \href{mailto:work@jxngrx.com}{work@jxngrx.com} \textbullet{}
        +91 9992990399 \textbullet{} Rohtak, Haryana \\
        \href{https://linkedin.com/in/jxngrx}{LinkedIn: jxngrx} \textbullet{}
        \href{https://jxngrx.com}{jxngrx.com} \textbullet{}
        \href{https://github.com/jxngrx}{GitHub: jxngrx} \textbullet{}
        \href{https://leetcode.com/jxngrx}{LeetCode: jxngrx}
    }
\end{center}

% ===== EXPERIENCE =====
\section*{Experience}


\textbf{Backend Developer (Freelance)} \\
\textit{Advan Drive} \hfill Dec 2025 -- Present  -- Remote
% \begin{itemize}
%     \item Architected a strongly typed \textbf{TypeScript} backend using \textbf{Node.js, Express, and MongoDB}, following a clean layered architecture.
%     \item Implemented social authentication (Google, Apple, Facebook) with secure token verification, JWT-based sessions, and role-aware request handling.
%     \item Designed a geo-aware presence and event lifecycle system using Google Place IDs, radius-based matching (\textbf{50–500m}), and TTL-based data expiration.
%     \item Built privacy-first APIs for discovery, connections, and event-scoped chats, enforcing access control, rate limiting, and abuse prevention.
% \end{itemize}

\begin{itemize}
    \item Built a strongly typed \textbf{TypeScript} backend with \textbf{Node.js, Express, MongoDB} using clean layered architecture.
    \item Implemented social auth (Google, Apple, Facebook) with token verification, JWT sessions, and role-based access.
    \item Designed geo-aware presence and event lifecycle using Place IDs, \textbf{50--500m} radius matching, and TTL expiry.
    \item Developed privacy-first APIs for discovery and chats with access control, rate limiting, and abuse protection.
    \item Modeled scalable schemas and indexes to support high-read discovery flows and low-latency queries.
\end{itemize}


\textbf{Software Development Engineer (Intern)} \\
\textit{Suffai} \hfill May 2024 -- Present | Remote
% \begin{itemize}
%     \item Migrated the React Native app to \textbf{Expo} and built a complete \textbf{dev $\rightarrow$ test $\rightarrow$ prod} release pipeline with OTA updates via Expo Updates and Notifications.
%     \item Took the product from \textbf{MVP to production}, independently owning mobile development for an app now serving \textbf{10K+ active users}.
%     \item Built and optimized \textbf{core backend business logic} including pricing calculations, cart flow, order lifecycle, and location-based operations.
%     \item Led end-to-end frontend execution—\textbf{UI/UX redesign, animations, cart flow}—and enhanced admin dashboards for orders, customers, and transactions, improving operational efficiency.
% \end{itemize}

\begin{itemize}
    \item Migrated the React Native app to \textbf{Expo} with a full \textbf{dev--test--prod} pipeline and OTA updates.
    \item Took the product from \textbf{MVP to production}, independently owning mobile development for \textbf{10K+ users}.
    \item Built core backend logic for pricing, cart flow, order lifecycle, and location-based operations.
    \item Led UI/UX redesign, animations, cart flow, and improved admin dashboards for orders and transactions.
    \item Integrated notifications, analytics, and monitoring to ensure release stability and production visibility.
\end{itemize}


\textbf{React Native App Developer (Contract)} \\
\textit{Tekora Labs — MeraNivas} \hfill Feb 2025 -- Dec 2025 | Remote
% \begin{itemize}
%     \item Owned end-to-end development of a \textbf{multi-role society management platform} (Super Admin, Admin, Residents, Security/Helpers) across \textbf{3 production apps} with shared architecture.
%     \item Implemented complex \textbf{navigation, notification, and permission flows} spanning finance, subscriptions, complaints, visitors, amenities, parking, and emergency modules.
%     \item Built \textbf{finance-critical systems} including invoice generation (maintenance \& events), analytics dashboards, budgets, fund settlements, and date-range exports.
%     \item Designed \textbf{automation and data systems}—subscription reminder cron jobs, attendance and QR-based visitor flows, bulk uploads, and scalable data models supporting audits and historical records.
% \end{itemize}

\begin{itemize}
    \item Owned end-to-end development of a \textbf{multi-role society platform} across \textbf{3 production apps}.
    \item Built navigation, notification, and permission flows for finance, subscriptions, visitors, parking, and emergencies.
    \item Implemented finance systems: invoicing, analytics, budgets, settlements, and date-range exports.
    \item Designed automation and data systems for reminders, attendance, QR visitors, bulk uploads, and audits.
    \item Coordinated releases and schema changes across apps to ensure backward compatibility and data integrity.
\end{itemize}



\textbf{App Developer (Contract)} \\
\textit{Figleo Web Services} \hfill Apr 2024 -- Oct 2024 | Remote
% \begin{itemize}
%     \item Built an offline-first visitor management system using AsyncStorage, boosting usage efficiency by \textbf{50\%}.
%     \item Reduced crash rates by \textbf{25\%} through Redux optimization and enhanced error boundaries.
%     \item Created QR/Barcode attendance scanner cutting check-in time by \textbf{70\%}.
% \end{itemize}

\begin{itemize}
    \item Built an offline-first visitor system using AsyncStorage, improving efficiency by \textbf{50\%}.
    \item Reduced app crashes by \textbf{25\%} through Redux optimization and error handling.
    \item Developed QR/Barcode attendance scanning, reducing check-in time by \textbf{70\%}.
\end{itemize}


% \textbf{Cybersecurity Intern} \\
% \textit{Gurugram Police Cyber Cell} \hfill Jun 2024 -- Jul 2024 | Gurugram
% \begin{itemize}
%     \item Contributed to solving \textbf{5 major cyber fraud cases} via digital forensics.
%     \item Performed threat analysis on 20+ devices, accelerating investigation timelines by \textbf{40\%}.
% \end{itemize}

% ===== PROJECTS =====
\section*{Projects}

% \textbf{Sarajod} (\href{https://github.com/jxngrx/sarajod_app_main}{GitHub})
% \hfill React Native, Node.js, MongoDB
% \begin{itemize}
%     \item Built a digital ledger app inspired by Khatabook for managing business transactions.
%     \item Implemented approval workflows similar to GitHub pull requests for multi-role verification.
% \end{itemize}

\textbf{ERohtak} (\href{https://erohtak.com}{Website})
\hfill React, RN, Node.js, MongoDB
\begin{itemize}
    \item Developed a multi-platform system with \textbf{100+ live business listings}, increasing partner sales by \textbf{20\%}.
    \item Built responsive UI with Jest test coverage, boosting user engagement by \textbf{35\%}.
\end{itemize}

\textbf{AI Support SaaS Platform}
(\href{https://github.com/jxngrx/jkdebug-echo-nextjs}{GitHub})
\hfill Next.js, Convex, VAPI, Clerk
\begin{itemize}
    \item Built B2B AI support system with real-time chat, voice AI, and RAG-based knowledge search.
    \item Implemented auto-resolution, human escalation, multi-workspaces, and team management.
    \item Integrated Clerk auth, subscription billing, secure AWS key storage, and an embeddable AI widget.
\end{itemize}

\textbf{RECHK} (\href{https://rechk.in}{Website})
\hfill Next.js, PostgreSQL, Python, Hugging Face
\begin{itemize}
    \item Built AI-driven research paper evaluation system reducing manual review time by \textbf{80\%}.
    \item Integrated ML models for plagiarism, grammar, and formatting analysis.
\end{itemize}

% ===== EDUCATION =====
\section*{Education}
\textbf{B.Tech in Computer Science}, Maharshi Dayanand University
\hfill Expected Jun 2026

% ===== SKILLS & CERTIFICATIONS =====
\begin{multicols}{2}

\section*{Skills}
\textbf{Languages:} TypeScript, SQL, JavaScript, Python \\
\textbf{Frameworks:} MERN Stack, React Native \\
\textbf{Databases:} Convex DB, PostgreSQL, MongoDB, MySQL \\
\textbf{Tools \& Platforms:} Git, Docker, Linux, Postman, AWS, GCP, Play Store Deployment, RabbitMQ

\columnbreak

\section*{Certifications}
Google Cloud Big Data \& ML Fundamentals \\
Foundations of Cybersecurity (Google) \\
Programming with JavaScript (Meta) \\
Modernizing Data Lakes (Google Cloud) \\
Docker: The Complete Guide

\end{multicols}

\end{document}
